Beyond Adaptive Web Design

### 2014-03-17 paper/paper.tex
feat: add saved traffic and page load times
feat: video motion detection experiment

\noindent We support 4 direction motion events: swipe from the left to the right, right to left, bottom to top and top to bottom. Using video motion detection we can enhance experience in websites and games. However we need a proper ambient lighting. There can be detection issues in too dark and too bright scenes.

@@

This approach works quite well for simple use cases. We can show multiple map types, markers or videos. However, more interactive elements require additional consideration. Even then use of an embedded elements directly still might not make sense because of unnecessary traffic. We can still use adaptive techniques to reduce it and replace basic static image with richer elements.

>>>>

\noindent We support 4 direction motion events: swipe from the left to the right, right to left, bottom to top and top to bottom. The experiment has been attended by hundreds of users. Using video motion detection we can enhance experience in websites and games. We can also detect device motion and orientation changes so it can be used as a supplementary input method to the accelerometer and gyroscope rotation. However we cannot take a full control over the webapp and need a proper ambient lighting. There can be detection issues in too dark and too bright scenes.

@@

Using adaptive web components we reduce initial traffic by 400 kB and a page load time by 350 ms for a youtube video in the average. For the map elemets the amount of saved traffic and load times are various and depend on element size. This approach works quite well for simple use cases. We can show multiple map types, markers or videos. However, more interactive elements require additional consideration. Even then use of an embedded elements directly still might not make sense because of unnecessary traffic. We can still use adaptive techniques to reduce it and replace basic static image with richer elements.
